\huge A Usability Evaluation of Tor Launcher

### 2017-03-15 pets2017-paper/pets2017-paper.tex
expand on methodology, switch setup and metrics sections, wordsmith to look pretty

\section{Methodology} 
This section discusses the process we used to evaluate the usability of Tor Launcher.

\subsection{Testing Pipeline} 
We began by performing a cognitive walkthrough~\cite{wharton1994cognitive,cognitive-walkthrough} to inspect the interface to anticipate potential problems and formally assess its pros and cons. A cognitive walkthrough is a formal method of inspection performed by researchers without any user involvement. We then conducted qualitative and quantitative usability tests. We believe both methods were necessary for a complete usability evaluation. Qualitative testing tells you {\it why or how} it is or is not usable, while quantitative testing tells you {\it how much} it is or is not usable. We used our observations from the qualitative study to design interface changes that would address common issues that these participants encountered. We used our quantitative testing setup to measure the usability of our proposed changes, as compared to the original Tor Launcher interface.

@@

\subsection{Evaluation Metrics}
\label{sec:eval}
We use the following industry-standard~\cite{albert2013measuring} metrics to determine if the launcher is usable: \\

@@

Completion rate is the fundamental usability metric that measures if users can accomplish the task. We defined success as a binary metric that is true if a user connected to Tor and false if a user did not. Task time is a supplemental usability metric that measures user productivity during the task. We measured this in two ways. Connection time measures how long users took to connect to Tor, while configuration time to measures how long users spent actively configuring bridges and proxies. We use both metrics to quantify productivity since the bootstrapping time, and hence, time spent waiting for the connection to succeed or fail, can dominate the measurement. Connection time is always greater than the configuration time, since it includes the configuration time.

\subsection{Experimental Setup}
\label{sec:environments}
We simulated three environments of varying censorship severity (Table~\ref{tab:environments}). We chose to 
simulate environments for the stability and reproducibility of the experiment, as real censored networks are volatile and complex.

>>>>

\section{Methodology} 
This section discusses the usability testing process used to evaluate Tor Launcher, the simulated censorship environments we used to require users to configure different network components to connect to Tor, and what our evaluation metrics  we collected to deem the interface usable or not usable.

\subsection{Testing Pipeline} 
We began by performing a cognitive walkthrough~\cite{wharton1994cognitive,cognitive-walkthrough} to inspect the interface to anticipate potential problems and formally assess its pros and cons. A cognitive walkthrough is a formal method of inspection performed by researchers without any user involvement. We then conducted qualitative and quantitative usability tests. We believe both methods were necessary for a complete usability evaluation. Qualitative testing tells you {\it why or how} it is or is not usable, while quantitative testing tells you {\it how much} it is or is not usable. We used our observations from the qualitative study to design interface changes that would address common issues that these participants encountered. We used our quantitative testing setup to measure the usability of our proposed changes, as compared to the original interface.

@@

\subsection{Experimental Setup}
\label{sec:environments}
We simulated three environments of varying censorship severity (Table~\ref{tab:environments}). We chose to 
simulate environments for the stability and reproducibility of the experiment, as real censored networks are volatile and complex. Re-routing participant traffic through other countries' networks also may introduce unforseen risks to the participants out of our control and performing hundreds of connections in short intervals during expeirments may draw unnecessary attention to Tor use in that country.

\subsection{Evaluation Metrics}
\label{sec:eval}
We use the following three industry-standard~\cite{albert2013measuring} usability metrics to quantify how easily users completed their task and if they were productive with their time: \\

@@

Completion rate is the fundamental usability metric that measures if users can accomplish the task. We defined success as a binary metric that is true if a user connected to Tor and false if a user did not. We consider this to be the most important usability metric, as this directly measures if users could connect to Tor.

Task time is a supplemental usability metric that measures user productivity during the task. We measured this in two ways. Connection time measures how long users took to connect to Tor, while configuration time to measures how long users spent actively configuring bridges and proxies. We use both metrics to quantify productivity since the bootstrapping time, and hence, time spent waiting for the connection to succeed or fail, can dominate the measurement. Connection time is always greater than the configuration time, since it includes the configuration time. We consider connection time and configuration time to be equally important in measuring user productivity.
